### 2024-06-04 acronyms/acronyms.tex
ies

vnewacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}

@@

@@

>>>>

\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}

@@

\newacronym{eis}{EIS}{Environmental Impact Statement}

@@

\newacronym{nep}{NEPA}{National Environmental Policy Act}
\newacronym{mca}{MC\&A}{Materials Control and Accountability}
\newacronym{rv}{R\&V}{Reproducibility \& Validation}
\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
